% SyncBox manual - Project files and build environment
% Written by Christopher Thomas.
%
% Copyright (c) 2021 by Vanderbilt University. This work is released under
% the Creative Commons Attribution-ShareAlike 4.0 International License.

\chapter{Project Files}
\label{sect-files}

\fixme{This is out of date as of December 2018.}

The following folders contain the CAD files, code, and documentation for 
the {\projectname} project:

\begin{center}
\begin{tabular}{lcl}
\textbf{sketch}     & ~~ & Arduino firmware working directory. \\
\textbf{hexfiles}   & ~~ & Arduino firmware binary releases. \\
\textbf{pcb}        & ~~ & Printed circuit board CAD files. \\
\textbf{manual}     & ~~ & User guide document files. \\
\textbf{schematics} & ~~ & Schematic drawings. Needed for the manual. \\
\textbf{datasheets} & ~~ & Datasheets for selected components. \\
\textbf{drawings}   & ~~ & Mechanical drawings. \\
\textbf{capture}    & ~~ & {\projectname} communications logs. \\
\end{tabular}
\end{center}

Relevant commentary is as follows:

\begin{itemize}
\item The ``sketch'' directory should be extracted (or symlinked) to a 
``neurarduino'' project directory within Arduino's ``sketchbook''. See the 
``README'' file in that directory for more commentary.

\item Alternatively, the ``sketch'' directory may be built using the
``neuravr'' library instead of using the Arduino development environment.
To do this, use ``make -f Makefile.neuravr''. See the ``README'' file in
the ``sketch'' directory for more commentary.

\item The ``pcb'' directory contains two subdirectories (``plots'' and 
``gerber''). The root directory contains the CAD file (edited with the 
``pcb'' CAD program from the gEDA project). The ``plots'' directory 
contains an automatically-generated postscript file and manually-generated 
XCF and PNG files. The ``gerber'' directory contains 
automatically-generated GBR files, and a script 
(``\texttt{pcb2seeed.sh}'') that converts these into a form SeeedStudio 
will accept (the ZIP archive in that directory).

\item The ``manual'' directory contains LaTeX source files for the user 
manual. Some resource files are symbolic links to files that are elsewhere 
in the project.

\item The ``schematics'' and ``datasheets'' directories contain 
human-readable information pertaining to the design of the {\projectname} 
system. Anyone redesigning the {\projectname} will likely want to read these.

\item The ``drawings'' directory contains mechanical drawings of the 
faceplate for the {\projectname} enclosure. The ``laser'' file is separated 
into layers in such a way as to facilitate importing into laser-cutter 
software.

\item The ``capture'' directory contains a sample conversation with the 
{\projectname}. Manually-extracted excerpts are used in the user manual. This 
file contains most types of traffic that will be seen when talking to the 
{\projectname}. It should be noted that echo was turned on during this 
conversation, which (prior to 2017) sometimes results in command characters
being interleaved with event data.
\end{itemize}

%
% This is the end of the file.
